Changelog

### 2021-05-25 changelog.tex
Updates from Overleaf

It is hard to explain Entropy. There is a rumor about entropy between John von Neumann and Claude Shannon. When Shannon developed the concept of information theory, he did not have a good idea to name the measurement of uncertainty in a system. Neumann told Shannon, ``You should call it entropy, for two reasons. In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name. In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.''

>>>>

It is hard to explain Entropy. There is a rumor about entropy between John von Neumann and Claude Shannon. When Shannon developed the concept of information theory, he did not have a good idea to name the measurement of uncertainty in a system. Neumann told Shannon, ``You should call it entropy, for two reasons. In the first place your uncertainty function has been used in statistical mechanics under that name, so it already has a name. In the second place, and more important, nobody knows what entropy really is, so in a debate you will always have the advantage.'' In my dissertation proposal, everyone does not really understand how we quantify the amount of leaked information in Abacus. In my final defense, everyone is confused with the term ``lower bounds'' except Dr. Wu.
